Inferring community characteristics in labelled networks

### 2021-05-23 nips/prelim.tex
Proof-read

\begin{definition}[Microcanonical DC-SBM]
	\label{defn:microcan-ndc-sbm}
	Let $N \in \Integers^{+}$ denote the number of vertices in an undirected graph. The block memberships are encoded by a vector $b \in [B]^N$,\footnote{We introduce the notation $[K] \coloneqq \{0, 1, 2 \dots K-1\}$ to compactly define a set of $K$ indices. Clearly, $[K]$ is only defined for $K \in \Integers^+$.}
	where $B \in \Integers^{+}$ is the number of non-empty blocks.
	Let $e \in (\Integers_0^+)^{N \times N}$ be the matrix of edge counts between blocks. $e_{rs}$ is then the number of edges from block $r$ onto block $s$ -- or twice that number if $r=s$. For undirected graphs $e$ is symmetric.
	Let $k \in (\Integers^+_0)^N$ be a vector denoting the degree sequence of the graph. $k_i$ is then the degree of vertex $i$.

	For the degree-corrected stochastic block model (DC-SBM), we say that the graph's adjacency matrix $A \in \{0,1\}^{N \times N}$ is generated as follows:
	%
	\begin{equation}
		A \sim \textrm{DC-SBM}_{\textrm{MC}} (b, e, k)
	\end{equation}
	%
	Where edges are placed uniformly at random but respecting the constraints imposed by $e$, $b$ and $k$ -- hence why this formulation is given the microcanonical moniker. Specifically, $A$ must satisfy the following:
	%
	\begin{equation}
		e_{rs} = \sum_{i, j} A_{ij} \one \{b_i = r\} \one \{b_j = s\} \qquad \textrm{and} \qquad
		k_i = \sum_j A_{ij}
	\end{equation}
	%
	The additional parameters $N$ and $B$ are omitted as they can be inferred from the shapes of $b$ and $e$.
\end{definition}

>>>>

\begin{definition}[Microcanonical DC-SBM]
	\label{defn:microcan-dc-sbm}
	Let $N \in \Integers^{+}$ denote the number of vertices in an undirected graph. The block memberships are encoded by a vector $b \in [B]^N$,\footnote{We introduce the notation $[K] \coloneqq \{1, 2 \dots K\}$ to compactly define a set of $K$ indices. Clearly, $[K]$ is only defined for $K \in \Integers^+$.}
	where $B \in \Integers^{+}$ is the number of non-empty blocks.
	Let $e \in (\Integers_0^+)^{N \times N}$ be the matrix of edge counts between blocks. $e_{rs}$ is then the number of edges from block $r$ onto block $s$ -- or twice that number if $r=s$. For undirected graphs $e$ is symmetric.
	Let $k \in (\Integers^+_0)^N$ be a vector denoting the degree sequence of the graph. $k_i$ is then the degree of vertex $i$.

	For the degree-corrected stochastic block model (DC-SBM), we say that the graph's adjacency matrix $A \in \{0,1\}^{N \times N}$ is generated as follows:
	%
	\begin{equation}
		A \sim \textrm{DC-SBM}_{\textrm{MC}} (b, e, k)
	\end{equation}
	%
	Where edges are placed uniformly at random but respecting the constraints imposed by $e$, $b$ and $k$ -- hence why this formulation is given the microcanonical moniker. Specifically, $A$ must satisfy the following:
	%
	\begin{equation}
		e_{rs} = \sum_{i, j} A_{ij} \one \{b_i = r\} \one \{b_j = s\} \qquad \textrm{and} \qquad
		k_i = \sum_j A_{ij}
		\label{eqn:sbm-constraints}
	\end{equation}
	%
	The additional parameters $N$ and $B$ are omitted as they can be inferred from the shapes of $b$ and $e$.
\end{definition}

In what follows, the SBM will always refer to the microcanonical DC-SBM variation.
